### 2014-11-11 tex/heap.tex
Halfway through describing heaps. Fixed several small typos, spacing issues, and errors

\section{Heap: A Bi-partiate Graph}

The heap in this work is a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
syntax in \figref{fig:machine-syntax} defines that graph in
$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
the set of location-constraint pairs in the heap associated with the
given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
the reference associated with the given location-field pair in the
heap.

@@

>>>>

\subsection{Heaps as Bipartite Graphs}
ADD REFERENCES ARE IMMUTABLE.
DEFINE $\rsym$ and $\rgse$.

A novel contribution is the representation of the heap with a labeled
bipartite graph consisting of references, $\cfgnt{r}$, and locations,
$\cfgnt{l}$. The machine syntax in \figref{fig:machine-syntax} defines
that graph in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the
reference map. As done with the environment, $\cfgnt{L}$ and
$\cfgnt{R}$ are treated as partial functions where $\cfgnt{L}(r) =
\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
the heap associated with the given reference, and
$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
associated with the given location-field pair in the heap.

@@

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$. 
\end{definition}

The rewrite rules that define the Javalite semantics are presented in
the supplemental document accompanying the paper.

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$. Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

### 2014-11-11 tex/javalite.tex
Halfway through describing heaps. Fixed several small typos, spacing issues, and errors

\section{Preliminaries}

\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is the
machine syntax. Javalite is syntactic machine defined as rewrites on a
string. The semantics use a CEKS model with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (K)ontinuation for what is to be executed next, and
a (S)tore for the heap.

\input{surface-syntax}

\subsection{Environment}
The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
value $\cfgnt{v}$. The value can be a reference, $\cfgnt{r}$ or one of
the special values $\cfgt{null}$, $\cfgt{true}$, or
$\cfgt{false}$. Although the Javalite machine is purely syntactic, for
clarity and brevity in the presentation, the more complex structures
such as the environment are treated as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
in the environment. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

>>>>

\section{Javalite}
The algorithm for generalized symbolic execution with symbolic heaps
is presented using Javalite. Javalite is a syntactic machine defined
as rewrites on a string \cite{saints-MS}. The semantics are small-step
using a CESK model with a (C)ontrol string representing the expression
being evaluated, an (E)nvironment for local variables, a (S)tore for
the heap, and a (K)ontinuation for what is to be executed next. The
semantics of the original Javalite machine, and its machine syntax,
are changed to reflect generalized symbolic execution and then
generalized execution with symbolic heaps.

The surface syntax (input) for Javalite is in
\figref{fig:surface-syntax} with the machine syntax (state) in
\figref{fig:machine-syntax}. Terminals are in bold face while
non-terminals are italicized. Ellipses indicate zero or more
repetitions. Tuples omit the commas for compactness. The language
itself uses s-expressions for convenience.

\input{surface-syntax}
\input{machine-syntax}

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$. Methods only take a single
parameter. Expressions, $\cfgnt{e}$, are somewhat typical with
$\cfgt{:=}$ indicating assignment, $\cfgt{=}$ indicating comparison,
$\cfgt{\$}$ as the dot-operator for field access, and $\cfgt{@}$ as
the dot-operator for method invocation. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as a return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values. It is assumed that only
type correct programs are given as input to the machine.

The state of the Javalite machine (\figref{fig:machine-syntax}),
$\cfgnt{s}$, includes the program registry, a pair of functions
defining the heap $\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a
constraint, $\phi$, defined over references in the heap, the
environment, $\eta$, for local variables, and the continuation
$\cfgnt{k}$. The more complex structures such as the environment are
defined as lists which start with empty, \cfgnt{mt}. The rewrite rules
that define the semantics treat these lists as partial
functions. As such, $\eta(\cfgnt{x}) = \cfgnt{r}$ is the
reference mapped to the variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is just like $\eta$ only the
variable $\cfgnt{x}$ now maps to $\cfgnt{v}$.

The continuation $\cfgnt{k}$ helps accomplish the small-step semantics
by indicating where the hole, $\cfgt{*}$, is located, by storing
temporary computations, and by keeping track of the next
computation. For example, the continuation
$\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$ indicates
that the machine is currently computing the expression for the object
reference on which the field $\cfgnt{f}$ is going to be accessed. Once
the field access is complete, the machine continues with $\cfgnt{k}$.

\input{heap}
